---
title: "Data Summaries"
author: "Aaron M. Shew"
date: "4/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Field-Year-Crop Summaries

The input data for this set of plots is from the summary_yield R script. The data primarily represent mean and standard deviation of field-crop-years for different variables. 

```{r data, warning=FALSE, echo=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(ggridges)
library(ggformula)
inputs <- read.csv("output/field-year-crop-inputs.csv")
```

### Histograms of SD of Applications 1-10

```{r SD Applications, echo=FALSE, warning=FALSE}

# App 1 Histogram
ggplot(inputs, aes(sd_App1)) +
  geom_histogram(binwidth = 10) +
  xlim(0,100) +
  ylim(0, 150) +
  ggtitle("SD of Application 1")

# App 2 Histogram
ggplot(inputs, aes(sd_App2)) +
  geom_histogram(binwidth = 10) +
  xlim(0,100) +
  ylim(0, 250)+
  ggtitle("SD of Application 2")

# App 3 Histogram
ggplot(inputs, aes(sd_App3)) +
  geom_histogram(binwidth = 10) +
  xlim(0,100) +
  ylim(0, 250)+
  ggtitle("SD of Application 3")

# App 4 Histogram
ggplot(inputs, aes(sd_App4)) +
  geom_histogram(binwidth = 10) +
  xlim(0,100) +
  ylim(0, 250)+
  ggtitle("SD of Application 4")

# App 5 Histogram
ggplot(inputs, aes(sd_App5)) +
  geom_histogram(binwidth = 10) +
  xlim(0,100) +
  ylim(0, 250)+
  ggtitle("SD of Application 5")

# App 6 Histogram
ggplot(inputs, aes(sd_App6)) +
  geom_histogram(binwidth = 10) +
  xlim(0,100) +
  ylim(0, 250)+
  ggtitle("SD of Application 6")

# App 7 Histogram
ggplot(inputs, aes(sd_App7)) +
  geom_histogram(binwidth = 10) +
  xlim(0,100) +
  ylim(0, 250)+
  ggtitle("SD of Application 7")

# App 8 Histogram
ggplot(inputs, aes(sd_App8)) +
  geom_histogram(binwidth = 10) +
  xlim(0,100) +
  ylim(0, 250)+
  ggtitle("SD of Application 8")

# App 9 Histogram
ggplot(inputs, aes(sd_App9)) +
  geom_histogram(binwidth = 10) +
  xlim(0,100) +
  ylim(0, 250)+
  ggtitle("SD of Application 9")

# App 10 Histogram
ggplot(inputs, aes(sd_App10)) +
  geom_histogram(binwidth = 10) +
  xlim(0,100) +
  ylim(0, 250)+
  ggtitle("SD of Application 10")
```

### Mean and SD of Yields

Mean yields show a little bi-modality for corn, which may be due to irrigation.

```{r echo=FALSE, warning=FALSE}
# Mean Yield
ggplot(inputs, aes(mean_yield)) +
  geom_histogram(binwidth = 10) +
  xlim(0,400) +
  #ylim(0, 250)+
  ggtitle("Mean Yield")+
  facet_wrap(~ CropName)

# SD Yield
ggplot(inputs, aes(sd_yield)) +
  geom_histogram(binwidth = 10) +
  xlim(0,200) +
  #ylim(0, 250)+
  ggtitle("SD of Yield")+
  facet_wrap(~ CropName)
```

### Yields vs Planting Date vs Applications

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Yield by Planting Date
ggplot(inputs, aes(x=mean_plant, y=mean_yield, color = factor(CropSeason))) +
  geom_point() +
  scale_color_viridis_d(option = "magma") +
  geom_smooth() + 
  ylim(0,300) +
  facet_wrap(~ CropName)+
  ggtitle("Mean Planting DOY by Mean Yield")

# Yield by SD of Application 1
ggplot(inputs, aes(x=sd_App1, y=mean_yield, color = factor(CropSeason))) +
  geom_point() +
  scale_color_viridis_d(option = "magma") +
  geom_smooth() + 
  ylim(0,500) +
  xlim(0,100)+
  facet_wrap(~ CropName)+
  ggtitle("Mean Yield by Mean Application 1")

# SD Yield by SD of Application 1
ggplot(inputs, aes(x=sd_App1, y=sd_yield, color = factor(CropSeason))) +
  geom_point() +
  scale_color_viridis_d(option = "magma") +
  geom_smooth() + 
  ylim(0,500) +
  xlim(0,100)+
  facet_wrap(~ CropName)+
  ggtitle("SD Yield by SD Application 1")

# Mean by SD of Application 1
ggplot(inputs, aes(x=sd_App1, y=mean_App1, color = factor(CropSeason))) +
  geom_point() +
  scale_color_viridis_d(option = "magma") +
  geom_smooth() + 
  ylim(0,500) +
  xlim(0,100)+
  facet_wrap(~ CropName)+
  ggtitle("SD Application 1 by Mean Application 1")

# Yield by SD of Application 2
ggplot(inputs, aes(x=sd_App2, y=mean_yield, color = factor(CropSeason))) +
  geom_point() +
  scale_color_viridis_d(option = "magma") +
  geom_smooth() + 
  ylim(0,500) +
  xlim(0,100)+
  facet_wrap(~ CropName)+
  ggtitle("Mean Yield by SD Application 2")

# Yield by SD of Application 2
ggplot(inputs, aes(x=sd_App2, y=sd_yield, color = factor(CropSeason))) +
  geom_point() +
  scale_color_viridis_d(option = "magma") +
  geom_smooth() + 
  ylim(0,500) +
  xlim(0,100)+
  facet_wrap(~ CropName)+
  ggtitle("SD Yield by SD Application 2")

# Mean by SD of Application 2
ggplot(inputs, aes(x=sd_App2, y=mean_App2, color = factor(CropSeason))) +
  geom_point() +
  scale_color_viridis_d(option = "magma") +
  geom_smooth() + 
  ylim(0,500) +
  xlim(0,100)+
  facet_wrap(~ CropName)+
  ggtitle("Mean Application 2 by SD Application 2")

# Mean by SD of Application 3
ggplot(inputs, aes(x=sd_App3, y=mean_App3, color = factor(CropSeason))) +
  geom_point() +
  scale_color_viridis_d(option = "magma") +
  geom_smooth() + 
  ylim(0,500) +
  xlim(0,100)+
  facet_wrap(~ CropName)+
  ggtitle("Mean Application 3 by SD Application 3")

# Mean Yield by SD of Application 3
ggplot(inputs, aes(x=sd_App3, y=mean_yield, color = factor(CropSeason))) +
  geom_point() +
  scale_color_viridis_d(option = "magma") +
  geom_smooth() + 
  ylim(0,500) +
  xlim(0,100)+
  facet_wrap(~ CropName)+
  ggtitle("Mean Yield by SD Application 3")

# SD Yield by SD of Application 3
ggplot(inputs, aes(x=sd_App3, y=sd_yield, color = factor(CropSeason))) +
  geom_point() +
  scale_color_viridis_d(option = "magma") +
  geom_smooth() + 
  ylim(0,500) +
  xlim(0,100)+
  facet_wrap(~ CropName)+
  ggtitle("SD Yield by SD Application 3")
```

